Improved Bounds for Online Balanced Repartitioning

### 2020-04-02 paper/paper.tex
todos
LB improvement by k-1

\noindent \textbf{Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the restricted model.
For the online model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $O(\ell^2)$~\cite{repartition-disc}.
%
Our algorithms can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The overview of results is in Table~\ref{tab:overview}.

@@

\maciek{Rename components in this section to adversary's components. Until the better name is figured out.}

@@

\begin{theorem}
  The competitive ratio of any deterministic online algorithm for \OBRP{} is in $\Omega(k\cdot \ell)$ for any $k\geq 3$.
  \maciek{TODO: the exact bound, not asymptotic}
\end{theorem}

@@

In our analysis, we distinguish among three types of clusters: $C_1, C_2, C_3$. In a cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.
Before bounding the competitive ratio of \TAlg, we introduce the lemma that estimates the cost of a single repartition of \TAlg. We defer its proof to Appendix~\ref{apx:omitted}.

>>>>

\noindent \textbf{Contributions.}
We provide an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the restricted model.
For the online model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $O(\ell^2)$~\cite{repartition-disc}.
%
Our algorithms can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.
The overview of known results is in Table~\ref{tab:overview}.

@@

@@

\begin{theorem}
  The competitive ratio of any deterministic online algorithm for \OBRP{} is in $\Omega(k\cdot \ell)$ for any $k\geq 3$.
  \maciek{TODO: the exact bound, not asymptotic}

  \maciek{The bound $(k \cdot \ell - k - \ell) / 2$ can be easily improved to $(k \cdot \ell - k - 1) / 2$ by playing a simple caching game in the first cluster, instead of just giving away the $k-1$ "blocker" (the caching game would build it gradually)}
\end{theorem}

@@

In our analysis, we distinguish among three types of clusters: $C_1, C_2, C_3$. In a cluster of type $C_i$, the size of the largest component contained in this cluster is $i$.
Before bounding the competitive ratio of \TAlg, we introduce the lemma that estimates the cost of a single repartition of \TAlg.
